Exploratory analysis of context: KL Divergence

### 2022-11-07 analysis/exploratory/context_versus_nocontext/rscripts/kl_divergence.Rmd
scripts and graphs

ggplot(data = agr, aes(x = Task, y=mean_kld, fill=ModalPresent)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=.25,
                position="dodge", 
                show.legend = FALSE) +
  facet_wrap(~Wh,ncol=2) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("graphs/denisty_kld_context_factors.pdf",width=6,height=6)
```

@@

>>>>

dodge = position_dodge(.9)
ggplot(data = agr, aes(x = Task, y=mean_kld, alpha=ModalPresent, fill=Task)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=.25,
                position="dodge", 
                show.legend = FALSE) +
  facet_wrap(~Wh,ncol=2) +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))

ggsave("../graphs/bar_kld_context_factors.pdf",width=5,height=6)
```

```{r}
dodge = position_dodge(.9)
ggplot(data = agr, aes(x = Wh, y=mean_kld, alpha=Task, fill=Wh)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),
                width=.25,
                position="dodge", 
                show.legend = FALSE) +
  facet_wrap(~ModalPresent,ncol=2) +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Task")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/bar_kld_context_factors_wh.pdf",width=6,height=3)

@@

## Interactions?
```{r}
# just recode the factors so that negative values are nocontext and positive values are context
kls.factors$Task <- as.factor(kls.factors$Task)
kls.factors$tgrep_id = as.factor(kls.factors$tgrep_id)
kls.factors$ModalPresent = as.factor(kls.factors$ModalPresent)
kls.factors$Wh = as.factor(kls.factors$Wh)

View(kls.factors)

d.kls.centered <- kls.factors %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(Task <- recode_factor(Task, context=1, nocontext=0)) %>%
  mutate(cTask = as.numeric(Task) - mean(as.numeric(Task))) %>% 
  droplevels()

contrasts(d.kls.centered$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

m.kld.full <- lmer(kld~cTask*Wh*cModalPresent + (1|tgrep_id), data=d.kls.centered)
summary(m.kld.full)
```
